---
title: 'ggplot2: Elegant Graphics for Data Analysis Hadley Wickham'
output:
  html_document:
    df_print: paged
---

[ggplot2: Elegant Graphics for Data Analysis
Hadley Wickham] (https://ggplot2-book.org/)


# {.tabset}

## I. Getting Started
```{r}
library(tidverse)
library(ggplot2)
library(remedy)

```

### 1. Introduction
#### 1.1 Welcome to ggplot2
#### 1.2 What is the grammar of graphics?
#### 1.3 How does ggplot2 fit in with other R graphics?
#### 1.4 About this book
#### 1.5 Installation
#### 1.6 Other resources
#### 1.7 Colophon

### 2. Getting started with ggplot2
#### 2.1 Introduction
#### 2.2 Fuel economy data
#### 2.3 Key components
##### 2.3.1 Exercises
####2.4 Colour, size, shape and other aesthetic attributes
##### 2.4.1 Exercises
####2.5 Facetting
##### 2.5.1 Exercises
#### 2.6 Plot geoms
##### 2.6.1 Adding a smoother to a plot
##### 2.6.2 Boxplots and jittered points
##### 2.6.3 Histograms and frequency polygons
##### 2.6.4 Bar charts
##### 2.6.5 Time series with line and path plots
##### 2.6.6 Exercises
#### 2.7 Modifying the axes
#### 2.8 Output

### 3. Frequently asked questions


## II. Toolbox

Introduction

### 4. Individual geoms
4.1 Basic plot types
### 5. Collective geoms
#### 5.1 Multiple groups, one aesthetic
#### 5.2 Different groups on different layers
#### 5.3 Overriding the default grouping
#### 5.4 Matching aesthetics to graphic objects
#### 5.5 Exercises

### 6. Statistical summaries
#### 6.1 Revealing uncertainty
#### 6.2 Weighted data
#### 6.3 Diamonds data
#### 6.4 Displaying distributions
##### 6.4.1 Exercises
#### 6.5 Dealing with overplotting
#### 6.6 Statistical summaries

### 7. Space and time
#### 7.1 Surface plots
#### 7.2 Drawing maps
##### 7.2.1 Vector boundaries
##### 7.2.2 Point metadata
##### 7.2.3 Raster images
##### 7.2.4 Area metadata

### 8. Annotations
#### 8.1 Titles
#### 8.2 Labels
#### 8.3 Text labels
#### 8.4 Building custom annotations
#### 8.5 Direct labelling
#### 8.6 Annotation across facets

### 9. Arranging plots
- patchwork
- cowplot for insets

## III. The Grammar

### 10. Mastering teh grammar
#### 10.1 Introduction
#### 10.2 Building a scatterplot
##### 10.2.1 Mapping aesthetics to data
##### 10.2.2 Scaling
#### 10.3 Adding complexity
#### 10.4 Components of the layered grammar
#### 10.5 Exercises

### 11. Building a plot layer by layer
#### 11.1 Introduction
#### 11.2 Building a plot
#### 11.3 Data
##### 11.3.1 Exercises
#### 11.4 Aesthetic mappings
##### 11.4.1 Specifying the aesthetics in the plot vs. in the layers
##### 11.4.2 Setting vs. mapping
##### 11.4.3 Exercises
#### 11.5 Geoms
11.5.1 Exercises
#### 11.6 Stats
##### 11.6.1 Generated variables
##### 11.6.2 Exercises
#### 11.7 Position adjustments
##### 11.7.1 Exercises

### 12. Scales, axes and legends
#### 12.1 Introduction

Scales control the mapping from data to aesthetics. They take your data and turn it into something that you can see, like size, colour, position or shape. Scales also provide the tools that let you read the plot: the axes and legends. Formally, each scale is a function from a region in data space (the domain of the scale) to a region in aesthetic space (the range of the scale). The axis or legend is the inverse function: it allows you to convert visual properties back to data.

You can generate many plots without knowing how scales work, but understanding scales and learning how to manipulate them will give you much more control. The basics of working with scales is described in Section 12.2. Section 12.3 discusses the common parameters that control the axes and legends. Legends are particularly complicated so have an additional set of options as described in Section 12.4. Section 12.5 shows how to use limits to both zoom into interesting parts of a plot, and to ensure that multiple plots have matching legends and axes. Section 12.6 gives an overview of the __different types of scales available in ggplot2, which can be roughly divided into four categories: continuous position scales, colour scales, manual scales and identity scales.__

#### 12.2 Modifying scales

A scale is required for every aesthetic used on the plot. When you write:

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point(aes(colour = class))
```
What actually happens is this:

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point(aes(colour = class)) +
  scale_x_continuous() + 
  scale_y_continuous() + 
  scale_colour_discrete()
```

Default scales are named according to the aesthetic and the variable type: scale_y_continuous(), scale_colour_discrete(), etc.

It would be tedious to manually add a scale every time you used a new aesthetic, so ggplot2 does it for you. But if you want to override the defaults, you’ll need to add the scale yourself, like this:

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point(aes(colour = class)) + 
  scale_x_continuous("A really awesome x axis label") +
  scale_y_continuous("An amazingly great y axis label")
```
The use of + to “add” scales to a plot is a little misleading. When you + a scale, you’re not actually adding it to the plot, but overriding the existing scale. This means that the following two specifications are equivalent:

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  scale_x_continuous("Label 1") +
  scale_x_continuous("Label 2")
#> Scale for 'x' is already present. Adding another scale for 'x', which will
#> replace the existing scale.

ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  scale_x_continuous("Label 2")
```

Note the message: if you see this in your own code, you need to reorganise your code specification to only add a single scale.

You can also use a different scale altogether:

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point(aes(colour = class)) +
  scale_x_sqrt() + 
  scale_colour_brewer()
```

You’ve probably already figured out the naming scheme for scales, but to be concrete, it’s made up of three pieces separated by "_":

1.scale
1.The name of the aesthetic (e.g., colour, shape or x)
1.The name of the scale (e.g., continuous, discrete, brewer).


```{r}
ggplot(mpg, aes(y = displ, x = class)) + 
  scale_y_continuous("Displacement (l)") + 
  # scale_x_discrete("Car type") +
  scale_x_discrete("Type of car") + 
  scale_colour_discrete() + 
  geom_point(aes(colour = drv)) + 
  scale_colour_discrete("Drive\ntrain")
```




##### 12.2.1 Exercises
#### 12.3 Guides: legends and axes
##### 12.3.1 Scale title
##### 12.3.2 Breaks and labels
##### 12.3.3 Exercises
#### 12.4 Legends
##### 12.4.1 Layers and legends
##### 12.4.2 Legend layout
##### 12.4.3 Guide functions
##### 12.4.4 Exercises
#### 12.5 Limits
##### 12.5.1 Exercises
#### 12.6 Scales toolbox
##### 12.6.1 Continuous position scales
##### 12.6.2 Colour
##### 12.6.3 The manual discrete scale
##### 12.6.4 The identity scale
##### 12.6.5 Exercises

### 13. Coordinate systems
#### 13.1 Linear coordinate systems
##### 13.1.1 Zooming into a plot with coord_cartesian()
##### 13.1.2 Flipping the axes with coord_flip()
##### 13.1.3 Equal scales with coord_fixed()
#### 13.2 Non-linear coordinate systems
##### 13.2.1 Transformations with coord_trans()
##### 13.2.2 Polar coordinates with coord_polar()
##### 13.2.3 Map projections with coord_map()

### 14. Facetting
#### 14.1 Facet wrap
#### 14.2 Facet grid
#### 14.3 Controlling scales
#### 14.4 Missing facetting variables
#### 14.5 Grouping vs. facetting
#### 14.6 Continuous variables
#### 14.7 Exercises
### 15. Themes
#### 15.1 Introduction
#### 15.2 Complete themes
##### 15.2.1 Exercises
#### 15.3 Modifying theme components
#### 15.4 Theme elements
##### 15.4.1 Plot elements
##### 15.4.2 Axis elements
##### 15.4.3 Legend elements
##### 15.4.4 Panel elements
##### 15.4.5 Facetting elements
##### 15.4.6 Exercises
#### 15.5 Saving your output


## IV. Extending ggplot2

### 16. Programming with ggplot2
#### 16.1 Introduction
#### 16.2 Single components
##### 16.2.1 Exercises
#### 16.3 Multiple components
##### 16.3.1 Plot components
##### 16.3.2 Annotation
##### 16.3.3 Additional arguments
##### 16.3.4 Exercises
#### 16.4 Plot functions
##### 16.4.1 Indirectly referring to variables
##### 16.4.2 The plot environment
##### 16.4.3 Exercises
#### 16.5 Functional programming
##### 16.5.1 Exercises

### 17 ggplot2 internals

#### 17.1 The plot() method
#### 17.2 Follow the data
##### 17.2.1 The build step
##### 17.2.2 The gtable step
#### 17.3 ggproto
##### 17.3.1 ggproto syntax
##### 17.3.2 ggproto style guide

### References